Honey Bee Colonies Impacted by Varroa, American Fouldbrood and Global Warming

### 2024-07-29 ManuscriptGrp10C07.28.2024.qmd
final draft manuscript

---
title: "Honey Bee Colonies Impacted by Varroa, American Fouldbrood and Global Warming"
subtitle: ""
author: Edward Cruz, Jr, Leonel G. Salazar, Amelia Tristan, Mojisola Popoola
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/apa.csl
---

@@

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
```

@@

@@

## General Background Information

@@

@@

```{r}
#| label: fig-schematic
#| fig-cap: "A figure that is manually generated and shows some overview/schematic. This has nothing to do with the data, it's just a random one from one of our projects I found and placed here."
#| echo: FALSE
knitr::include_graphics(here("assets","antigen-recognition.png"))
```

@@

```{r}
library(readxl)
library(tidyverse)

@@

data <- read.csv("C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/docs/DatabyState.csv")

View(data)
```

# Select all columns except 3, 6, and 9
Data_Clean <- dplyr::select(data, -c(3, 6, 9))

# Output cleaned data file to a csv file.
write.csv(Data_Clean, "C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/docs/Databystate_Clean.csv")

view(Data_Clean)

```{r}
library(readxl)
library(tidyverse)

data <- read.csv("C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/docs/DatabyState.csv")

# Select all columns except 3, 6, and 9
Data_Clean <- dplyr::select(data, -c(3, 6, 9))

# Output cleaned data file to a csv file.
write.csv(Data_Clean, "C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/docs/Databystate_Clean.csv")

# Assuming your data frame is named "data"

# Filter for rows where "Loss" or "Deadout" is present in any column (case-insensitive)
library(stringr)  # Load stringr package for regular expressions
data_filtered <- Data_Clean[rowSums(sapply(data, grepl, pattern = c("Loss"), ignore.case = TRUE)) > 0, ]

# Output cleaned data file to a csv file.
write.csv(Data_Clean, "C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/docs/Databystate_Filtered.csv")

```{r}
ggplot(data_filtered, aes( Data.Item, State.ANSI)) + geom_boxplot()
```

```{r}
ggplot(data_filtered, aes(Year)) + geom_histogram()
```

```{r}
ggplot(data_filtered, aes(x = Year)) + 
  geom_histogram(bins = 10, fill = "blue", color = "black", alpha = 0.7) +  # Adding fill color, border color, and transparency
  labs(title = "Histogram of Year", x = "Year", y = "Count") +  # Adding labels
  theme_minimal() 
```

@@

```{r}
library(readxl)
update.packages("tidyverse")
library(tidyverse)
update.packages("dplyr")
library(dplyr)
update.packages('mgcv')
library(mgcv)
```

```{r}
# Output cleaned data file to a csv file.
hcny_data <- read.csv("C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/docs/hcny_CleanDraft.csv", header = FALSE, stringsAsFactors = FALSE)
```

@@

```{r}
# Convert specified columns to numeric
hcnydata_cleaned <- hcnydata_cleaned %>%
  mutate(across(c("Varroa_Mites", "Other_Parasites_1/", "Disease_2/", "Pesticides", "Other_3/", "Unknown"), as.numeric))
```

@@

```{r}
ggplot(hcnydata_cleaned, aes(Varroa_Mites)) + geom_histogram()
```

```{r}
ggplot(hcnydata_cleaned, aes(x = Varroa_Mites)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  labs(title = "Histogram of Varroa Mites",
       x = "Varroa Mites",
       y = "Frequency")
```

```{r}
# Example scatter plot of two variables
ggplot(hcnydata_cleaned, aes(x = Varroa_Mites, y = "Desease_2/")) +
  geom_point() +
  labs(title = "Scatter Plot of Varroa Mites vs Disease",
       x = "Varroa Mites",
       y = "2 American and European Foul Brood")
```

```{r}
# Write the cleaned data to a new CSV file
write.csv(hcnydata_cleaned, "C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/docs/hcnydata_cleaned.csv", row.names = FALSE)
```

\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*Conclusion- all code below is test code right now\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*\*

## Statistical analysis

@@

@@

@@

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Data summary table."
#| echo: FALSE
resulttable=readRDS("../../results/tables/summarytable.rds")
knitr::kable(resulttable)
```

@@

@fig-result shows a scatterplot figure produced by one of the R scripts.

```{r}
#| label: fig-result
#| fig-cap: "Height and weight stratified by gender."
#| echo: FALSE
knitr::include_graphics(here("results","figures","height-weight-stratified.png"))
```

@@

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Linear model fit table."
#| echo: FALSE
resulttable2 = readRDS(here("results","tables","resulttable2.rds"))
knitr::kable(resulttable2)
```

>>>>

---
title: "Honey Bee Colonies Impacted by Varroa, American Fouldbrood and Global Warming"
subtitle: ""
author: Edward Cruz, Jr, Leonel G. Salazar, Amelia Tristan, Mojisola Popoola
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
---

@@

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(ggplot2)
library(dplyr)
library(scales)
library(showtext)
library(ggimage)
```

@@

```{r}
# Create a data frame with the composition of honey
honey_data <- data.frame(
  component = c("Fructose", "Glucose", "Water", "Maltose", "Trisaccharides, Carbohydrates", "Sucrose", "Minerals, Vitamins, Enzymes"),
  percentage = c(38.5, 31.0, 17.1, 7.2, 4.2, 1.5, 0.5)
)

# Define colors for the segments
honey_data$color <- c("#FFA726", "#FB8C00", "#FFD54F", "#FFB74D", "#90CAF9", "#F06292", "#BA68C8")

# Plot with ggplot2
ggplot(honey_data, aes(x = "", y = percentage, fill = component)) +
  geom_bar(width = 0.8, stat = "identity", color = "white") +
  coord_polar("y", start = 0) +
  scale_fill_manual(values = honey_data$color) +
  geom_text(aes(x= 1.8,label = paste0(percentage, "%")), position = position_stack(vjust = 0.6), size = 3, color = "black") +
  labs(
    title = "COMPOSITION OF HONEY",
    subtitle = "Illustration of honey components by percentage",
    fill = NULL
  ) +
  theme_void() +
  theme(
    plot.title = element_text(size = 22, face = "bold", hjust = 0.5, family = "lobster"),
    plot.subtitle = element_text(size = 14, hjust = 0.5),
    legend.position = "bottom",
    legend.text = element_text(size = 12)
  )
```

@@

You can add options to executable code like this

```{r}
library(ggplot2)
library(sf)
library(maps)
```

```{r}
states <- st_as_sf(map("state", plot = FALSE, fill = TRUE))

```{r}
varroa_data <- data.frame(
  state = c("alabama", "alaska", "arizona", "arkansas", "california", "colorado", 
            "connecticut", "delaware", "florida", "georgia", "hawaii", "idaho", 
            "illinois", "indiana", "iowa", "kansas", "kentucky", "louisiana", 
            "maine", "maryland", "massachusetts", "michigan", "minnesota", 
            "mississippi", "missouri", "montana", "nebraska", "nevada", "new hampshire", 
            "new jersey", "new mexico", "new york", "north carolina", "north dakota", 
            "ohio", "oklahoma", "oregon", "pennsylvania", "rhode island", 
            "south carolina", "south dakota", "tennessee", "texas", "utah", 
            "vermont", "virginia", "washington", "west virginia", "wisconsin", "wyoming"),
  year = c("1986 - 1987", "1988 - 1989", "1990 - 1991", "1992 - 1993", "1994 - 1995",
           "1986 - 1987", "1988 - 1989", "1990 - 1991", "1992 - 1993", "1994 - 1995",
           "1986 - 1987", "1988 - 1989", "1990 - 1991", "1992 - 1993", "1994 - 1995",
           "1986 - 1987", "1988 - 1989", "1990 - 1991", "1992 - 1993", "1994 - 1995",
           "1986 - 1987", "1988 - 1989", "1990 - 1991", "1992 - 1993", "1994 - 1995",
           "1986 - 1987", "1988 - 1989", "1990 - 1991", "1992 - 1993", "1994 - 1995",
           "1986 - 1987", "1988 - 1989", "1990 - 1991", "1992 - 1993", "1994 - 1995",
           "1986 - 1987", "1988 - 1989", "1990 - 1991", "1992 - 1993", "1994 - 1995",
           "1986 - 1987", "1988 - 1989", "1990 - 1991", "1992 - 1993", "1994 - 1995",
           "1986 - 1987", "1988 - 1989", "1990 - 1991", "1992 - 1993", "1994 - 1995")
)

```{r}
states <- merge(states, varroa_data, by.x = "ID", by.y = "state", all.x = TRUE)

```{r}
ggplot(data = states) +
  geom_sf(aes(fill = year), color = "#292929", size = 0.2) +
  scale_fill_manual(
    values = c(
      "1986 - 1987" = "#CD2626", 
      "1988 - 1989" = "#CD9B1D", 
      "1990 - 1991" = "#FFD700", 
      "1992 - 1993" = "#00CD00", 
      "1994 - 1995" = "#104E8B"
    ),
    na.value = "#757575"
  ) +
  theme_minimal() +
  labs(
    title = "Spread of Varroa Mites",
    fill = "Year of First Appearance"
  )

Written By:sdns6mchl4. (2016, February 24). Varroa mite spread in the United States. Beesource Beekeeping Forums. https://www.beesource.com/threads/varroa-mite-spread-in-the-united-states.365462/ \## General Background Information

[**Uncapped Honey Floresville,Texas Hive**]{.underline}

![](images/Bee%20Frame%202024-01.jpg){width="674"}

[**Capped Honey one Month Later same hive frame- Italian bees Floresville, Texas**]{.underline}

![](images/Bee%20Frame%20Capped%20Honey.jpg){fig-align="center" width="697"}

@@

[**Bacterium Infection Foul Brood.**]{.underline}

![](images/American-Foul-Brood-Comb-1024x768-1.jpg)

[**Dead bees resulting from extreme heat found in hive**]{.underline}.

![](images/dead-bees-hive-colony-collapse-600nw-2289939105.webp){width="679"}

@@

```{r}
#| label: fig-schematic
#| fig-cap: "A figure that is manually genera#ted and shows some overview/schematic. This has nothing to do with the data, it's just a random one #from one of our projects I found and placed here."
#| echo: FALSE
#knitr::include_graphics(here("assets","antigen-recognition.png"))
```

@@

```{r}
library(readxl)
library(tidyverse)
library(ggplot2)
library(knitr)
```

@@

data <- read.csv("C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/DatabyState.csv")
```

```{r}
View(data)
```

```{r}
# Select all columns except 3, 6, and 9
Data_Clean <- dplyr::select(data, -c(3, 6, 9))
```

```{r}
# Output cleaned data file to a csv file.
write.csv(Data_Clean, "C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/Databystate_Clean.csv")
```

```{r}
view(Data_Clean)
```

```{r}
data <- read.csv("C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/DatabyState.csv")
```

```{r}
# Select all columns except 3, 6, and 9
Data_Clean <- dplyr::select(data, -c(3, 6, 9))
```

```{r}
# Output cleaned data file to a csv file.
write.csv(Data_Clean, "C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/Databystate_Clean.csv")
```

```{r}
# Assuming your data frame is named "data"
# Filter for rows where "Loss" or "Deadout" is present in any column (case-insensitive)
library(stringr)  # Load stringr package for regular expressions
data_filtered <- Data_Clean[rowSums(sapply(data, grepl, pattern = c("Loss"), ignore.case = TRUE)) > 0, ]
```

```{r}
# Output cleaned data file to a csv file.
write.csv(Data_Clean, "C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/Databystate_Filtered.csv")
```

```{r}
view(Data_Clean)
```

```{r}
ggplot(data_filtered, aes( Data.Item, State.ANSI)) + geom_boxplot()
```
STATE ANSI IS THE CODE FOR STATE BY PERIOD AND YEAR. VALUE IS COUNT.

The above data set is organized by year, state, period of the year, type of loss, and count. There are only three observed years, with observations from 2015 to 2017. Loss by collapse disorder describes a colony that losses a majority of its worker bees. Loss by deadout describes a loss of the entire colony: workers, drones, larvae, pupa, and queen. The bar chart shown below depicts loss count by type and period. The periods roughly follow North American seasons; April through June is spring, January through March is winter, July through September is summer, and October through December is fall. We can observe a pattern in the losses increasing in the first half of the year (January through June), while losses decrease the second half. This could suggest that as the weather warms, colonies are affected by the increasing heat.
```{r}
ggplot(data_filtered, aes(Year)) + geom_histogram()
```
The above data set is organized by year, state, period of the year, type of loss, and count. There are only three observed years, with observations from 2015 to 2017. Loss by collapse disorder describes a colony that losses a majority of its worker bees. Loss by deadout describes a loss of the entire colony: workers, drones, larvae, pupa, and queen. The bar chart shown below depicts loss count by type and period. The periods roughly follow North American seasons; April through June is spring, January through March is winter, July through September is summer, and October through December is fall. We can observe a pattern in the losses increasing in the first half of the year (January through June), while losses decrease the second half. This could suggest that as the weather warms, colonies are affected by the increasing heat
```{r}
ggplot(data_filtered, aes(x = Year)) + 
  geom_histogram(bins = 10, fill = "blue", color = "black", alpha = 0.7) +  # Adding fill color, border color, and transparency
  labs(title = "Histogram of Year", x = "Year", y = "Count") +  # Adding labels
  theme_minimal() 
```

@@

```{r}
library(readxl)
library(tidyverse)
library(dplyr)
library(mgcv)
```

```{r}
# Output cleaned data file to a csv file.
hcny_data <- read.csv("C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/hcny_CleanDraft.csv", header = FALSE, stringsAsFactors = FALSE)
```

```{r}
head(hcny_data)
```
This gives us the properties of out data set
```{r}
str(hcny_data)
```

@@

```{r warning=FALSE}
# Convert specified columns to numeric
hcnydata_cleaned <- hcnydata_cleaned %>%
  mutate(across(c("Varroa_Mites", "Other_Parasites_1/", "Disease_2/", "Pesticides", "Other_3/", "Unknown"), as.numeric))
```

@@

```{r}
ggplot(hcnydata_cleaned, aes(Varroa_Mites)) + geom_histogram()
```
The above indicated the count of Varroa Mites in our data
From our project, we found that varroa mites are the top cause for colony loss. Four states had the highest levels of varroa cases and were chosen for comparison, in the United States: Wisconsin, Texas, Ohio, and Pennsylvania. The box plot below shows one outlier in this top 5 areas, with the average being just above 50.
```{r}
ggplot(hcnydata_cleaned, aes(x = Varroa_Mites)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  labs(title = "Histogram of Varroa Mites",
       x = "Varroa Mites",
       y = "Frequency")
```

```{r}
# Example scatter plot of two variables
ggplot(hcnydata_cleaned, aes(x = Varroa_Mites, y = "Desease_2/")) +
  geom_point() +
  labs(title = "Scatter Plot of Varroa Mites vs Disease",
       x = "Varroa Mites",
       y = "2 American and European Foul Brood")
```
The above plot illustrates the comparison between American and European Foul Brood and Varroa Mites
```{r}
view(hcnydata_cleaned)
```

```{r}
# Write the cleaned data to a new CSV file
write.csv(hcnydata_cleaned, "C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/hcnydata_cleaned.csv", row.names = FALSE)
```

```{r}
# Output cleaned data file to a csv file.
hcny_data <- read.csv("C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/hcny_CleanDraft.csv", header = FALSE, stringsAsFactors = FALSE)
```

```{r}
# Step 2: Merge the first two rows to create a new header
new_header <- paste(hcny_data[1, ], hcny_data[2, ], sep = " ")

# Step 3: Set the new header
colnames(hcny_data) <- new_header

# Step 4: Remove the first three rows
hcny_data <- hcny_data[-c(1:3), ]

# Step 5: Remove completely blank rows
hcny_data <- hcny_data[rowSums(hcny_data != "") > 0, ]

# Display the resulting data frame
head(hcny_data)
```

```{r}
# Assuming hcny_data is your cleaned data frame
colnames(hcny_data) <- c("state", "varroa_mites", "other_pests", "disease", "pesticides", "other", "unknown")
```

```{r}
# Convert specified columns to numeric with warning suppression
hcnydata_cleaned <- hcny_data %>%
  mutate(across(c("varroa_mites", "other_pests", "disease", "pesticides", "other", "unknown"), ~suppressWarnings(as.numeric(.))))

# Display the resulting data frame
head(hcnydata_cleaned)
```

```{r,message=FALSE, warning=FALSE}
ggplot(hcnydata_cleaned, aes(varroa_mites)) + geom_histogram()
```

![](images/_20220406_on_varroadestructor_minden_00463080.jpg){fig-align="center" width="541"}

```{r}
view((hcnydata_cleaned))
```

```{r}
# Write the cleaned data to a new CSV file
write.csv(hcnydata_cleaned, "C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/hcny_CleanDraft.csv", row.names = FALSE)
```

```{r}
# Assuming hcnydata_cleaned is your data frame
hcnydata_cleaned <- hcnydata_cleaned[apply(hcnydata_cleaned, 1, function(x) !all(is.na(x))), ]

# Print the modified data frame to verify the changes
head(hcnydata_cleaned)
view(hcnydata_cleaned)
```

```{r}
str(hcnydata_cleaned)
```

```{r, message=FALSE}
#update.packages('mgcv')
library(mgcv)
```

```{r}
# Convert the 'state' column to a factor
hcnydata_cleaned$state <- as.factor(hcnydata_cleaned$state)

# Display the resulting data frame
head(hcnydata_cleaned)
```

```{r}
# Step 3: Reindex the rows starting from 1
rownames(hcnydata_cleaned) <- NULL
```

```{r}
# Identify the rows to exclude
rows_to_exclude <- c(46)

# Remove rows 45 to 52 while excluding row 46
data_hcny <- hcnydata_cleaned[-c(45:52)[-which(c(45:52) %in% rows_to_exclude)], ]
```

```{r}
library(ggplot2)

# Create a bar graph to show state and varroa_mites
ggplot(data = data_hcny, aes(x = state, y = varroa_mites)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Varroa Mites by State",
       x = "State",
       y = "Varroa Mites Count") +
  theme_minimal() +
  coord_flip()
```
T
Varroa Mite

![](images/Varrpa%201.webp){fig-align="center" width="307"}

![](images/varroa-mite-bee.webp){fig-align="center" width="286"}
The above image shows the count of Varroa Mites by States.Colorado and North Dakota comes highest in the plot with Oklahoma and New Mexico the lowest in count.
This indicated that we have more of Varroa Mites in North Dakota and Colorado compared to Oklahoma and New Mexico
## Statistical analysis

@@

[**`Texas Bee gathering pollen from natural Texas foliage`**]{.underline}

![](images/Bee%20Feeding.jpg){fig-align="center" width="609"}

@@

# Remove all rows with any NA values

library(tidyr)
library(dplyr)

my_data <- data_hcny %>% drop_na()

# Verify that NAs have been removed
glimpse(my_data)
```

# Bivariate Analysis

```{r, message=FALSE, warning=FALSE}
## Example of a bivariate plot between 'state' and 'varroa_mites'
ggplot(my_data, aes(x = disease, y = varroa_mites)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Bivariate Relationship between State and Varroa Mites",
       x = "State",
       y = "Varroa Mites")
```
From the above graph we see that Varroa Mites concentrated more in certain states than others
# Multivariable GLM

```{r}
#install.packages("tidymodels")
library(tidymodels)
library(broom)
library(stats)
library(MASS)
# Specify the GLM model
glm_spec <- linear_reg() %>%
  set_engine("glm")

# Create a recipe for preprocessing the data
glm_recipe <- recipe(varroa_mites ~ other_pests + disease + pesticides + other + unknown, data = my_data) %>%
  step_normalize(all_predictors())

# Create a workflow
glm_workflow <- workflow() %>%
  add_model(glm_spec) %>%
  add_recipe(glm_recipe)

# Fit the model
glm_fit <- fit(glm_workflow, data = my_data)

# Print the model summary using tidy()
model_summary <- tidy(glm_fit)
print(model_summary)
```

@@

@@

@fig-result shows a scatterplot figure produced by one of the R scripts.
```{r}
plot <- ggplot(my_data, aes(x = varroa_mites , y =  other_pests + disease + pesticides + other + unknown )) +
  geom_point(color = "blue") +              # Scatter plot
  geom_smooth(method = "lm", color = "red") + # Regression line
  ggtitle("Scatter Plot with Linear Regression Line") +
  xlab("varroa_mites") +
  ylab("other_pests + disease + pesticides + other + unknown")
print(plot)
```
The above diagram indicates that varroa mites are proportionally related to other psests, diseases, pesticides and other unknown parasite

@@

```{r}
saveRDS(my_data, file = "my_data.rds")
```

```{r}
file.exists("my_data.rds")
```

```{r}
getwd()
```

```{r}
loaded_data <- readRDS("my_data.rds")
print(loaded_data)
```

```{r}
my_data <- readRDS("my_data.rds")

```{r}
model <- lm(varroa_mites ~ other_pests + disease + pesticides + other + unknown, data = my_data)
```

```{r}
summary(model)
```
From the linear regression  we see that only 49% of variation in the data can be explained by varroa mites, The p value is 0.01 which is statistically significant
```{r}
library(broom)
library(knitr)
```

```{r}
model_tidy <- tidy(model)
```

```{r}
kable(model_tidy, caption = "Linear Model Fit Table")
```
The p value for varroa Mites is statistically significant at 0.009 when compared with other disease or pesticides.
